Sting nematodes modify metabolomic profiles of host plants

### 2019-10-22 manuscript/sci-rep/reviewer-letter/reviewer-response.tex

Line 58. The authors stated that the canonical correspondence analysis explained 42\% of the observed inertia in the total metabolome. I suggest that the authors explain this because in Figure 2 this analysis explained 71.9\% of the total metabolome variation (CCA1: 45.3\% + CCA2: 26.6\%).

\begin{quote}
  \textit{Thanks for your inquiry.  Canonical correspondence analysis did explain 42\% of the observed inertia.  Of that 42\% explained inertia, axis 1 explained 45.3\% and axis 2 26.6\%.  Summing the explained variation of the other 3 axis with the first two would result in 100\% of the variation captured in canonical ordination or 42\% of observed inertia (constrained $\chi^2$) in the total metabolome. This explanation has been elaborated upon in the text.   } 
\end{quote}

Lines 146 and 150. Change ‘conetainers’ to ‘containers and container’

\begin{quote}
    \textit{Thanks for suggesting this. Conetainers should be Cone-tainers to refer to the specific type of container used to house the plants.  We have clarified this in the Methods section adding both information about the company from which they can be procured and changing the spelling in lines 148 and 150 for clarification.  }
\end{quote}

### 2019-10-22 manuscript/sci-rep/nature-plants.tex
author feedback on reviewer response

Three African bermudagrass (\textit{Cynodon transvaalensis} Burtt-Davy) lines were used to evaluate metabolomic responses to pathogen infection.  One susceptible line (AB03), one tolerant line (AB39), and one line with moderate tolerance (AB33) were stolon propagated and allowed to establish for 30 days in 3.8cm diameter, 21cm deep UV-stabilized Ray Leach Cone-tainers filled with 100ml USGA grade sand followed with a soil plug (to prevent sand leakage). Plants were grown in a climate controlled greenhouse at 25\textsuperscript{o}C and 50\% RH under a 11:13 light:dark cycle.  Plants were watered twice daily for 5 minutes and received 24-8-16 NPK liquid fertilizer on a weekly basis.  Sting nematode (\textit{Belonolaimus longicaudatus} Rau) originally collected from Florida turf and reared on \textit{C. transvaalensis} were used in bioassays.

@@

To evaluate the effects of nematode infection on bermudagrass metabolite response, treated plants in containers were inoculated with 50 sting nematodes of mixed age and gender per container.  Control (noninoculated) plants did not receive any nematode treatment. Seven replications of each line (AB03, AB33, AB39) and treatment (inoculated, noninoculated) combination were conducted.  Ninety days following nematode inoculation (time enough for nematode growth and reproduction), plants were removed from the container, the soil plug removed, and the 100ml of sand gently rinsed to extract the nematodes for further processing through centrifugal flotation and counting on an inverted microscope.  Rinsed roots were placed in 50ml falcon tubes then immersed in liquid nitrogen and stored at -80\textsuperscript{o}C until lyophilization.  Lyophilzed roots were weighed and samples selected for metabolomics analysis.

>>>>

Three African bermudagrass (\textit{Cynodon transvaalensis} Burtt-Davy) lines were used to evaluate metabolomic responses to pathogen infection.  One susceptible line (AB03), one tolerant line (AB39), and one line with moderate tolerance (AB33) were stolon propagated and allowed to establish for 30 days in 3.8cm diameter, 21cm deep UV-stabilized Ray Leach Cone-tainers (SC10; Stuewe & Sons, Inc., Tangent, OR) filled with 100ml USGA grade sand followed with a soil plug (to prevent sand leakage). Plants were grown in a climate controlled greenhouse at 25\textsuperscript{o}C and 50\% RH under a 11:13 light:dark cycle.  Plants were watered twice daily for 5 minutes and received 24-8-16 NPK liquid fertilizer on a weekly basis.  Sting nematode (\textit{Belonolaimus longicaudatus} Rau) originally collected from Florida turf and reared on \textit{C. transvaalensis} were used in bioassays.

@@

To evaluate the effects of nematode infection on bermudagrass metabolite response, treated plants in Cone-tainers were inoculated with 50 sting nematodes of mixed age and gender per Cone-tainer.  Control (noninoculated) plants did not receive any nematode treatment. Seven replications of each line (AB03, AB33, AB39) and treatment (inoculated, noninoculated) combination were conducted.  Ninety days following nematode inoculation (time enough for nematode growth and reproduction), plants were removed from the container, the soil plug removed, and the 100ml of sand gently rinsed to extract the nematodes for further processing through centrifugal flotation and counting on an inverted microscope.  Rinsed roots were placed in 50ml falcon tubes then immersed in liquid nitrogen and stored at -80\textsuperscript{o}C until lyophilization.  Lyophilzed roots were weighed and samples selected for metabolomics analysis.
